% \lettrine{}{} command typesets a drop cap in the document

% second brace set formats text placed inside as small caps
% (same thing as doing \lettrine{L}\textsc{orem ipsum ...}

\chapter{Bros Before Hoes}
\label{Article1-bros-before-hoes}
\vspace{30pt}
    % \lettrine{T}{\textbf{he Principle of Bros Before Hoes Dictates that,}}
    \noindent
    \textbf{\Large{\begin{quote}
        \lettrine{A}{} Bro is bound by the highest order of Bro Law to prioritise the needs, wants, and emergencies of another Bro over any and all engagements with women, irrespective of circumstance or consequence.
    \end{quote}}}

% \vspace{20pt}
\newpage

\lettrine{}{\underline{\textbf{\large{Extension to the Law}}}}\vspace{5pt}

The following clauses reinforce the obligatory nature of this law:
\begin{enumerate}
    \item \textbf{Clause 1: The Universal Priority Mandate:}  
    No event, social gathering, romantic dinner, or life milestone shall take precedence over a Bro in need. This includes, but is not limited to: first dates, anniversaries, and even one’s own wedding.

    \item \textbf{Clause 2: The Conflict of Interest:}
    In the event that two Bros find themselves pursuing the same romantic interest, both are compelled by this sacred code to immediately withdraw from said pursuit, prioritising their brotherhood over transient desires. Following this withdrawal, the Bros must partake in a symbolic act of reconciliation—be it a toast, a fist bump, or a shared plate of wings.

    \item \textbf{Clause 3: The Girlfriend Scenario:}  
    A Bro must answer the call of another Bro, even when in the presence of a significant other. Should the girlfriend object, it is the Bro’s duty to politely inform her: \textit{“It’s The Bro Code, non-negotiable.”}

    \item \textbf{Clause 4: The Wife Immunity:}  
    While society may expect a Bro to place his wife first, the Bro Code operates above societal norms. A Bro shall make every effort to attend to his Bro, utilising excuses, diversions, and, if necessary, fake emergencies to maintain the bond.

    \item \textbf{Clause 5: The Wife Extension:}  
    If the bro’s presence is required solely due to his wife’s friend’s company, the Bro Code reasserts dominance. The bro must exit gracefully under any pretence, citing \textit{“Urgent Bro Business”}.

    \item \textbf{Clause 6: The Random Encounter Clause:}  
    In interactions involving unknown women, \textit{“a random broad you came across”}, the original law is applied in its purest form—Bros are prioritised, period.

    \item \textbf{Clause 7: The Emergency Amplifier:}  
    Should the calling Bro use the phrase \textit{“Bro, this is serious”} the summoned Bro must drop anything and everything, regardless of context, and arrive within the shortest possible time frame—no questions asked.
\end{enumerate}
\vspace{25pt}
% \newpage

\label{Article1-Repercussions}\lettrine{}{\underline{\textbf{\large{Repercussions for Violations}}}}\vspace{5pt}

Should the summoned Bro be deemed guilty of breaching this sacred law, one or multiple repercussions may be imposed. The aggrieved Bro reserves the full right to select the consequence(s) or appoint a trusted delegate to make the selection on their behalf. 
\\

\textbf{\textit{In all cases, a mandatory face-to-face apology must be delivered at the very next encounter, without exception.}}\\

\noindent
The Repercussions are as follows:
\begin{enumerate}
    \item \textbf{The Drink Penalty:}
    The offending Bro shall provide a minimum of two drinks of the aggrieved Bro’s choosing, at a venue and time determined solely by the wronged Bro.

    \item \textbf{Acts of Service:}
    The offending Bro shall provide Acts of Service towards the aggrieved Bro. However, these depends on the severity of the crime committed\footnote{Matters involving seduction of women and matters affecting coitus, holds utmost importance. (\textit{e.g. wingman duties or last minute drugstore trips, yes you guessed it correctly.})}. These are, but not limited to:
    \begin{itemize}
        \item \textbf{Chauffeuring Duties:}
        The offending Bro shall be required to provide transportation services to the aggrieved Bro, including but not limited to the fulfillment of designated driver duties or late-night retrieval services. The duration of such obligations can vary.

        \item \textbf{Social Buffering:}
        In the event of social discomfort, awkward encounters, or ill-fated engagements, the offending Bro is hereby obligated to serve as the primary exit strategist or conversational diversionary agent. Furthermore, should the aggrieved Bro determine that the situation necessitates immediate extraction, the offending Bro shall, without objection, facilitate said extraction by any means necessary, up to and including, the faking of one’s own demise, as deemed appropriate by the aggrieved Bro.
    \end{itemize}

    \item \textbf{The Nickname Decree:}
    The offending Bro will be assigned a light-hearted, but mildly humiliating nickname (\textit{e.g. “Captain Bail” or “The Flake”}) for a period of 48 hours.

    \item \textbf{Right to Amend:}
    In the event that the aggrieved Bro deems the prescribed penalties insufficient or unsatisfactory, the aggrieved Bro reserves the unequivocal right to propose an alternative repercussion. Such alternative measures must be proportionate to the gravity of the offense.
\end{enumerate}

\vspace{25pt}

\lettrine{}{\underline{\textbf{\large{Example}}}}\vspace{5pt}

\begin{quote}
    \tt{
        \small{
            It’s 8:30 PM. Ted is mid-way through an anniversary dinner with his girlfriend, candles lit, dessert en route. Suddenly, Barney calls, voice tense, “Ted, I need you. I am on a date and I have spotted Crazy Eyes, help.”\\\\ \noindent Without hesitation, Ted turns to his girlfriend, offers a sincere “It’s Bro Code. Non-negotiable,” and leaves. He arrives at the date venue, makes up an excuse to get barney out, assumes wingman duties at the nearest Pub, and ensures Barney's success. Later, the girlfriend—still mildly annoyed—accepts a peace offering of flowers and chocolates and an explanation she’ll never fully understand.\\\\ \noindent Failure to respond in such a scenario would have resulted in the invocation of the \hyperref[Article1-Repercussions]{Repercussions}, costing Ted two overpriced cocktails, a chauffeuring duty, and potentially the nickname “Sir Bails-a-Lot” for 48 hours.
        }
    }
\end{quote}